UbiComp 2012 Conference Proceedings Format

### 2012-05-15 report/ubicomp2012.tex
ubicom template

\documentclass{ubicomp2011}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Your Title}, pdfauthor={Your Authors}, pdfkeywords={your
keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true, }
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}

@@

% use this command to override the default ACM copyright statement
% (e.g. for preprints). Remove for camera ready copy.
%\toappear{Submitted for review to UbiComp 2011.}

\title{UbiComp 2011 Conference Proceedings Format}
\numberofauthors{2}
\author{
  \alignauthor First Author Name (Blank for Blind Review)\\
    \affaddr{Affiliation  (Blank for Blind Review)}\\
    \affaddr{Address  (Blank for Blind Review)}\\
    \email{e-mail address (Blank for Blind Review)}
 \alignauthor Second Author Name (Blank for Blind Review)\\
    \affaddr{Affiliation  (Blank for Blind Review)}\\
    \affaddr{Address  (Blank for Blind Review)}\\
    \email{e-mail address (Blank for Blind Review)}  }
\maketitle

\begin{abstract}
  In this paper we describe the formatting requirements for the UbiComp 2011
  Conference Proceedings, and offer recommendations on writing for the
  worldwide Ubiquitous Computing readership.  Please review this document even if
  you have submitted to Ubiquitous Computing conferences before, for some format
  details have changed relative to previous years. These include the
  formatting of table captions, the formatting of references, a
  requirement to include ACM DL indexing information, and guidelines for how to handle relevant references to your own work while preparing your submission for blind review.
\end{abstract}

>>>>

\documentclass{ubicomp2012}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Your Title}, pdfauthor={Your Authors}, pdfkeywords={your
keywords}, bookmarksnumbered, pdfstartview={FitH}, colorlinks,
citecolor=black, filecolor=black, linkcolor=black, urlcolor=black,
breaklinks=true, }
\newcommand{\comment}[1]{}
\definecolor{Orange}{rgb}{1,0.5,0}
\newcommand{\todo}[1]{\textsf{\textbf{\textcolor{Orange}{[[#1]]}}}}

@@

% use this command to override the default ACM copyright statement
% (e.g. for preprints). Remove for camera ready copy.
%\toappear{Submitted for review to UbiComp 2012.}

\title{UbiComp 2012 Conference Proceedings Format}
\numberofauthors{2}
\author{
  \alignauthor First Author Name (Blank for Blind Review)\\
    \affaddr{Affiliation  (Blank for Blind Review)}\\
    \affaddr{Address  (Blank for Blind Review)}\\
    \email{e-mail address (Blank for Blind Review)}
 \alignauthor Second Author Name (Blank for Blind Review)\\
    \affaddr{Affiliation  (Blank for Blind Review)}\\
    \affaddr{Address  (Blank for Blind Review)}\\
    \email{e-mail address (Blank for Blind Review)}  }
\maketitle

\begin{abstract}
  In this paper we describe the formatting requirements for the UbiComp 2012
  Conference Proceedings, and offer recommendations on writing for the
  worldwide Ubiquitous Computing readership.  Please review this document even if
  you have submitted to Ubiquitous Computing conferences before, for some format
  details have changed relative to previous years. These include the
  formatting of table captions, the formatting of references, a
  requirement to include ACM DL indexing information, and guidelines for how to handle relevant references to your own work while preparing your submission for blind review.
\end{abstract}
